PRISM protocol v0.3

### 2021-10-12 prism-backend/research/article.tex
Completed section on connector e2ee protocol.

\begin{description}
\item[Code secrecy.] Codes exchanged via a QR code are always confidential.
  Note that this is trivial, as it is exchanged via a secure channel, and
  the holder never sends it back in the clear.
\item[Code injectivity.] Every QR code that is received by a holder, allegedly
  sent by an issuer, was sent before by that issuer. Again, this is trivial due
  to the secure channel used to exchange the QR code.
\item[Holder's public key authenticity.] Every message received by an issuer
  in step 3, containing a public key for key-exchange usage, that was
  allegedly sent by a holder, was indeed previously sent by that holder.
  This is ensured through the message authentication code (MAC) that
  leverages the random QR code exchanged via the secure channel, which is
  only known to the issuer and the holder.
\item[Holder's public key injectivity.] For every session in which an
  issuer receives in step 3 a message, allegedly sent by a holder in
  step 2, containing the holder's public key, it was that holder, in
  the same session, who sent the public key in step 2.  
\item[Credential secrecy.] This property has two variants: it ensures
  secrecy for credentials sent by an honest issuer to a holder that was honest
  at the moment of sending the credential, and is not compromised afterwards;
  and it also ensures secrecy for credentials received by an honest holder,
  allegedly from an honest issuer, if both holder and issuer were honest when
  the credential is received, and they are not corrupted afterwards. Altogether
  with the credential authenticity property shown next, it ensures that only
  (honest) holder and issuer learn the contents of a credential.
\item[Credential authenticity.] All messages containing a credential, received
  by a holder at step 5, where indeed sent by an issuer and addressed to that
  same holder, as long as both issuer and holder keys are not compromised.
\item[Credential non-injectivity.] All messages containing a credential, received
  by a holder at step 5, were sent by an issuer and addressed to that holder
  at step 4. Note, however, that both messages in steps 4 and 5 dont necessarily
  pertain to the  same ``session'' (in instantiations where parallel sessions
  may occur). However, this does not pose a risk, as in any case, the messaged
  is sent by the issuer, and received by the intended holder.
\end{description}

>>>>

\begin{description}
\item[Code secrecy.] Codes exchanged via a QR code are always confidential.
  Note that this is trivial, as it is exchanged via a secure channel, and
  the holder never sends it back in the clear.
\item[Code injectivity.] Every QR code that is received by a holder, allegedly
  sent by an issuer, was sent before by that issuer. Again, this is trivial due
  to the secure channel used to exchange the QR code.
\item[Holder's public key authenticity.] Every message received by an issuer
  in step 3, containing a public key for key-exchange usage, that was
  allegedly sent by a holder, was indeed previously sent by that holder.
  This is ensured through the message authentication code (MAC) that
  leverages the random QR code exchanged via the secure channel, which is
  only known to the issuer and the holder.
\item[Holder's public key injectivity.] For every session in which an
  issuer receives in step 3 a message, allegedly sent by a holder in
  step 2, containing the holder's public key, it was that holder, in
  the same session, who sent the public key in step 2.  
\item[Credential secrecy.] This property has two variants: it ensures
  secrecy for credentials sent by an honest issuer to a holder that was honest
  at the moment of sending the credential, and is not compromised afterwards;
  and it also ensures secrecy for credentials received by an honest holder,
  allegedly from an honest issuer, if both holder and issuer were honest when
  the credential is received, and they are not corrupted afterwards. Altogether
  with the credential authenticity property shown next, it ensures that only
  (honest) holder and issuer learn the contents of a credential.
\item[Credential authenticity.] All messages containing a credential, received
  by a holder at step 5, where indeed sent by an issuer and addressed to that
  same holder, as long as both issuer and holder keys are not compromised.
\item[Credential non-injectivity.] All messages containing a credential, received
  by a holder at step 5, were sent by an issuer and addressed to that holder
  at step 4. Note, however, that both messages in steps 4 and 5 don't necessarily
  pertain to the  same ``session'' (in instantiations where parallel sessions
  may occur). However, this does not pose a risk, as in any case, the messaged
  is sent by the issuer, and received by the intended holder.
\end{description}
